% --------------------------------------------------------------
% Andrew Tindall
% --------------------------------------------------------------
 
\documentclass[12pt]{article}
 
\usepackage[margin=1in]{geometry} 
\usepackage{amsmath,amsthm,amssymb,enumitem,hyperref,tikz-cd}

\newcommand{\N}{\mathbb{N}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\e}{\varepsilon}
\newcommand{\bs}{\backslash}
\newcommand{\PGL}{\text{PGL}}
\newcommand{\Sp}{\text{Sp}}
\newcommand{\tr}{\text{tr}}
\newcommand{\Lie}{\text{Lie}}
\newcommand{\rec}[1]{\frac{1}{#1}}
\newcommand{\toinf}{\rightarrow \infty}


\theoremstyle{definition}
\newtheorem{proofpart}{Part}
\newtheorem{theorem}{Theorem}
\makeatletter
\@addtoreset{proofpart}{theorem}
\makeatother


\newenvironment{problem}[2][Problem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
 
\begin{document}
 
%\renewcommand{\qedsymbol}{\filledbox}
 
\title{Midterm Notes}
\author{Andrew Tindall}
 
\maketitle
Construct the fundamental groupoid of a space $X$ as a category whose objects are the elements of $X$ and whose morphisms are homotopy classes of paths from point to point - this is a well-defined category, as concatenation of paths is well-defined and associative up to homotopy class.
\par A \textbf{Normal Cover} of a space $X$ is a cover $\rho: \tilde X \to X$ with the property that 
\[ \forall x \in X, \forall x_0, x_1 \in \rho^{-1}(x), \exists \text{deck transformation }\alpha: \tilde X \to X, \text{s.t.} \alpha(x_{0}) = x_1\]
Recall that a deck transformation is a homeomorphism of covers, $\rho \simto \rho$. The group of deck transformations is transitive in its action on any fiber of $X$. A normal deck transformation is exactly one such that the projection of the fundamental group of the cover to the fundamental group of $X$ along the functor $\rho_*$ is a normal subgroup of the fundamental group of $X$. 
\par There do exist non-normal covers. For example, the cover of $\R \mathbb P^n$ by a sequence of spheres  with copies of the projective space at the end is not normal, because there is no deck transformation taking one of the endpoints to one of the points sandwiched in between spheres - they do not have homeomorphic neighborhoods. Equivalently, we can say that the subgroup of $\Z_2 \times \Z_2$ corresponding to this cover is not normal. What subgroup is it, exactly? Who
knows.
\par Deformation retract vs. strong deformation retract: just ``deformation retract'' means ahomotopy of paths which takes the identity to a map whose image is some closed subgroup $A$ of our space $X$, and is the identity when restricted to $A \times \left\{ 1 \right\}$. A strong deformation retract is one which is also constant on $A$ along the whole homotopy. Strong deformation retracts will not be important in this class, since we have been focusing on simple contractibility.
\par Proposition 1.32 tells us that the fundamental group of a pointed space $X$, quotiented by the image of the fun. gp. of a cover, is in bijection with the set of points in the fiber over the basepoint of $X$. In particular, in the cover of real projective space by the $n$-sphere, we have a $2$-sheeted cover, and the fundamental group of the cover is trivial, since it is the universal cover. So the fund. gp. of projective $n$-space is of order 2, and $\Z_2$ is the only such group.
\par Recall that SEMI-locally simply-connected is equivalent to requiraing that each point in $X$ has a neighborhood where the image of the fundamental group of the neighborhood is trivial in the fundamental group of $X$. NOT necessarily that this neighborhood itself have trivial fundamental group, but that it trivializes when mapped into the larger group. In contrast, to be locally simply connected would require that the neighborhood be simply connected itself
\end{document}
