% --------------------------------------------------------------
% Andrew Tindall
% --------------------------------------------------------------
 
\documentclass[12pt]{article}
 
\usepackage[margin=1in]{geometry} 
\usepackage{amsmath,amsthm,amssymb,enumitem,tikz-cd}

\newcommand{\N}{\mathbb{N}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\e}{\varepsilon}
\newcommand{\bs}{\backslash}
\newcommand{\PGL}{\text{PGL}}
\newcommand{\Sp}{\text{Sp}}
\newcommand{\tr}{\text{tr}}
\newcommand{\Lie}{\text{Lie}}
\newcommand{\rec}[1]{\frac{1}{#1}}
\newcommand{\toinf}{\rightarrow \infty}


\theoremstyle{definition}
\newtheorem{proofpart}{Part}
\newtheorem{theorem}{Theorem}
\makeatletter
\@addtoreset{proofpart}{theorem}
\makeatother


\newenvironment{problem}[2][Problem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
 
\begin{document}
 
%\renewcommand{\qedsymbol}{\filledbox}
 
\title{Homework 11}
\author{Andrew Tindall\\
Algebra II}
 
\maketitle
\begin{problem}{1}
	Dummit \& Foote, 10.5.5: Let $A_1$ and $A_2$ be $R$-modules. Prove that $A_1 \oplus A_2$ is a flat $R$-module if and only if both $A_1$ and $A_2$ are flat. More generally, prove that an arbitrary direct sum $\sum A_i$ of $R$-modules is flat if and only if each $A_i$ is flat.
	\begin{proof}
		We use the following fact: the tensor product commutes with arbitrary direct sums. This follows immediately from the fact that the tensor product is left-adjoint to the Hom functor, and the fact that the direct sum is a colimit in the category $R$-mod, since left-adjoints commute with colimits.
		\par Let 
		\[\begin{tikzcd}&0 \arrow[r,""]  &L \arrow[r, " \psi"]&M \arrow[r, " \phi"] &N \arrow[r,""] & 0\end{tikzcd}\]
		be an exact sequence of $R$-modules. We wish to show that the direct sum $\bigoplus_{i \in I} A_i$ is exact; it suffices to show that the sequence
		\[\begin{tikzcd}&0 \arrow[r] & L \otimes \left( \bigoplus_{i\in I}A_i \right) \arrow[r, "\psi \otimes \text{Id}"] &M \otimes \left( \bigoplus_{i\in I}A_i \right) \arrow[r, "\phi \otimes \text{Id}"] & N\otimes (\bigoplus_{i\in I} A_i) \arrow[r] &0 \end{tikzcd}\]
		is exact. By the fact that $\otimes$ commutes with $\oplus$, this sequence is equivalent to
		\[\begin{tikzcd}&0 \arrow[r] &\bigoplus_{i\in I}(L \otimes A_i) \arrow[r, "\bigoplus(\psi \otimes \text{Id})"] &\bigoplus_{i\in I}(M \otimes A_i)\arrow[r, "\bigoplus(\phi \otimes \text{Id})"]&\bigoplus_{i\in I}(N \otimes A_i)\arrow[r]&0.\end{tikzcd}\]
		We want to see that $\text{Im}(\bigoplus(\psi \otimes \text{Id})) = \text{Ker}(\bigoplus(\phi \otimes \text{Id}))$. This holds, at least in the finite case, but I will not prove it here.	
		\end{proof}
\end{problem}
\begin{problem}{2}
	10.5.7: Let $A$ be a nonzero finite abelian group.
	\begin{enumerate}[https://en.wikipedia.org/wiki/Deadmau5#2017%E2%80%93present:_Stuff_I_Used_to_Do,_Where's_the_Drop?,_Polar_soundtrack_and_Mau5villelabel=\alph*.]
		\item Prove that $A$ is not a projective $\Z$-module.
		\item Prove that $A$ is not an injective $\Z$-module.
			\begin{proof}
				\begin{enumerate}[label=\alph*.]
					\item We know that $A$ is a finite product of cyclic abelian groups:
						\[A \cong \Z/a_1\Z \oplus \dots \oplus \Z/a_n\Z\]
						However, by Corrolary 10.5.31, A finitely generated module is projective if and only if it is a direct summand of a finitely generated free module. However, if $A$ were a submodule of a free $\Z$-module, it could not have any elements of finite order. Every element of $A$ has finite order (at most $\text{lcm}(a_1, \dots , a_n)$), so $A$ cannot be projective.
					\item By $10.5.26$, a module $A$ over a P.I.D. is injective if and only if $rA = A$ for every nonzero $r \in R$. In this case, this requirement means that there can be no torsion. Since any finite abelian group is torsion, $A$ cannot be injective.
				\end{enumerate}
			\end{proof}
	\end{enumerate}
\end{problem}
\end{document}
